Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants\thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN 712689 SC$^2$.}

### 2017-05-05 cav2017/cav2017.tex
define Ts
tidying

\begin{figure*}[t]
\centering
\includegraphics[width=0.6\textwidth]{ct.eps}
\vspace{0.1cm}
\caption{Completeness threshold for multi-staged verification \blue{[Explain meaning of Ts, which I don't think is introduced anywhere in the current draft.]}}
\label{fig:ct}
\end{figure*}

@@

In the subsequent iteration, the synthesizer is unable to find further 
suitable candidates and it returns UNSAT, meaning that the current precision is
insufficient.  Consequently, we increase the precision to $I_p=17$,
$F_p=7$. \blue{[ Explain how precision is increased, byte-congruent.]}
%
Since the previous counterexamples were obtained at lower precision,
we remove them from the set of counterexamples.  Back in the {\sc
  synthesize} phase, we re-start the process with a candidate solution
with all coefficients $0$.  Next, the {\sc safety} verification stage
provides the first counterexample at higher precision, $x_0=[-0.5
  \ 0.5 \ 0.5]$ and {\sc synthesize} finds $K=[0 \ 0.01171875
  \ 0.015625]^T$ as a candidate that eliminates this counterexample.
However, this candidate triggers the counterexample
$x_0=[0.5\ -0.5\ -0.5]$ found again by the {\sc safety} verification
stage.  In the next iteration, we get the candidate $K=[0 \ 0
  \ -0.015625]$, followed by the counterexample $x_0 = [0.5 \ 0.5
  \ 0.5]$. Finally, {\sc synthesize} finds the candidate $K=[0.01171875
  \ -0.013671875 \ -0.013671875]^T$, which is validated as a final
solution by all verification stages.

@@

The proof of Jury's criterion~\cite{fadali} relies on the fact that the relationship between states and
next states is defined by $x_{k+1} = (A_d - B_dK) x_k$, all computed
at infinite precision.  When we employ a FWL digital controller, the
operation becomes:
%
\begin{align*}
x_{k+1} &= A_d \cdot x_{k} -(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  \\
x_{k+1} &= (A_d  - B_dK) \cdot x_k + B_dK\delta, 
%\\ x_{k+1}&=A_d x_{k} + B_du_{k}
\end{align*}
%
where $\delta$ is the maximum error that can be introduced by the FWL
controller in one step, i.e., by reading the states values once and
multiplying by $K$ once.  We derive the closed form expression for $x_n$ as
follows:
%
\begin{align*}
x_{1} &= (A_d  - B_dK)x_0 + B_dK\delta \\
x_{2} &= (A_d  - B_dK)((A_d  - B_dK)x_0 + B_dK\delta ) + B_dK\delta \\
      &=(A_d  - B_dK)^2x_0 + (A_d  - B_dK)B_dK\delta + B_dK\delta \\
%x_{3}  &=(A_d  - B_dK)^3x_0 + (A_d  - B_dK)^2B_dK\delta + (A_d  - B_dK)B_dK\delta + B_dK\delta\\
x_{n} &= (A_d  - B_dK)^nx_0 + (A_d  - B_dK)^{n-1}B_dK\delta + ... + (A_d  - B_dK)^1B_dK \delta + B_dK\delta \\
  &= (A_d - B_dK)^nx_0 + \sum_{i=0}^{i=n-1}(A_d - B_dK)^iB_dk\delta. 
\end{align*}

@@

To show that a fixed-point implementation of the same controller will
converge to a finite value, we need to show that the infinite sum converges. 
A known result is that a power series of matrices
converges~\cite{horn1990matrix}, iff the eigenvalues of the matrix are less
than~1, as follows:
%
%\begin{align*}
$\sum_{i=0}^{\infty}T^i  = (I - T)^{-1}$, 
%\end{align*}
%
where $I$ is the identity matrix and $T$ is a square matrix. Thus, our system will converge to the value 
%
\begin{align*}
0 + (I - A_d + B_dK)^{-1}B_dk\delta \,. 
\end{align*}
%
As a result, if the value $(I - A_d + B_dK)^{-1}B_dk\delta$ is within the
safe space, then the synthesized fixed-point controller results in a safe
closed-loop model.  The convergence to a finite value, however, will not
make it asymptomatically stable.

>>>>

\begin{figure*}[t]
\centering
\includegraphics[width=0.6\textwidth]{ct.eps}
\vspace{0.1cm}
\caption{Completeness threshold for multi-staged verification. $T_s$ is the time step for the time discretization of the control matrices.}
\label{fig:ct}
\end{figure*}

@@

In the subsequent iteration, the synthesizer is unable to find further 
suitable candidates and it returns UNSAT, meaning that the current precision is
insufficient.  Consequently, we increase the precision the plant is modelled with to $I_p=17$,
$F_p=7$. We increase the precision by 8 bits each step in order to be compliant with the CBMC type API.
%
Since the previous counterexamples were obtained at lower precision,
we remove them from the set of counterexamples.  Back in the {\sc
  synthesize} phase, we re-start the process with a candidate solution
with all coefficients $0$.  Next, the {\sc safety} verification stage
provides the first counterexample at higher precision, $x_0=[-0.5
  \ 0.5 \ 0.5]$ and {\sc synthesize} finds $K=[0 \ 0.01171875
  \ 0.015625]^T$ as a candidate that eliminates this counterexample.
However, this candidate triggers the counterexample
$x_0=[0.5\ -0.5\ -0.5]$ found again by the {\sc safety} verification
stage.  In the next iteration, we get the candidate $K=[0 \ 0
  \ -0.015625]$, followed by the counterexample $x_0 = [0.5 \ 0.5
  \ 0.5]$. Finally, {\sc synthesize} finds the candidate $K=[0.01171875
  \ -0.013671875 \ -0.013671875]^T$, which is validated as a final
solution by all verification stages.

@@

The proof of Jury's criterion~\cite{fadali} relies on the fact that the relationship between states and
next states is defined by $x_{k+1} = (A_d - B_dK) x_k$, all computed
at infinite precision.  When we employ a FWL digital controller, the
operation becomes:
%
\begin{align*}
x_{k+1} &= A_d \cdot x_{k} -(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  \\
x_{k+1} &= (A_d  - B_dK) \cdot x_k + B_dK\delta, 
%\\ x_{k+1}&=A_d x_{k} + B_du_{k}
\end{align*}
%
where $\delta$ is the maximum error that can be introduced by the FWL
controller in one step, i.e., by reading the states values once and
multiplying by $K$ once.  We derive the closed form expression for $x_n$ as
follows:
%
\begin{align*}
x_{1} &= (A_d  - B_dK)x_0 + B_dK\delta \\
x_{2} %&= (A_d  - B_dK)((A_d  - B_dK)x_0 + B_dK\delta ) + B_dK\delta \\
 &=(A_d  - B_dK)^2x_0 + (A_d  - B_dK)B_dK\delta + B_dK\delta \\
%x_{3}  &=(A_d  - B_dK)^3x_0 + (A_d  - B_dK)^2B_dK\delta + (A_d  - B_dK)B_dK\delta + B_dK\delta\\
x_{n} &= (A_d  - B_dK)^nx_0 + (A_d  - B_dK)^{n-1}B_dK\delta + ... + (A_d  - B_dK)^1B_dK \delta + B_dK\delta \\
  &= (A_d - B_dK)^nx_0 + \sum_{i=0}^{i=n-1}(A_d - B_dK)^iB_dk\delta. 
\end{align*}

@@

%T%o show that a fixed-point implementation of the same controller will
%converge to a finite value, we need to show that the infinite sum converges. 
The power series of matrices
converges~\cite{horn1990matrix} iff the eigenvalues of the matrix are less
than~1 as follows:
%
%\begin{align*}
$\sum_{i=0}^{\infty}T^i  = (I - T)^{-1}$, 
%\end{align*}
%
where $I$ is the identity matrix and $T$ is a square matrix. Thus, our system will converge to the value 
%
\begin{align*}
0 + (I - A_d + B_dK)^{-1}B_dk\delta \,. 
\end{align*}
%
As a result, if the value $(I - A_d + B_dK)^{-1}B_dk\delta$ is within the
safe space, then the synthesized fixed-point controller results in a safe
closed-loop model.  The convergence to a finite value, however, will not
make it asymptomatically stable.
